Leveraged Volume Sampling - Summary

### 2019-03-02 summary/paper-summary.tex
added a brief about the main idea behind the proof of theorem 8

>>>>

        To prove the first property, the paper demonstrates:
        \begin{equation}
            E(||\frac{1}{k}U^TQ_{\pi}r - U^Tr||^2) = r^TE((\frac{1}{k}Q_{\pi}-I)UU^T(\frac{1}{k}Q_{\pi}-I))r \leq ||E((\frac{1}{k}Q_{\pi}-I)UU^T(\frac{1}{k}Q_{\pi}-I))||||r||^2
        \end{equation}
        And proceeds to bound $||E((\frac{1}{k}Q_{\pi}-I)UU^T(\frac{1}{k}Q_{\pi}-I))||$ via a clever application of a Hadamard Product inequality.
